DaLi: Database as a Library

### 2017-02-20 paper/dali.tex
OpSem added to the paper.
Last version that is made for Queue.
Locus definition
Motivation.

%% Some recommended packages.
\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption

@@

>>>>

%% Some recommended packages.
\usepackage{mathtools}
\usepackage{mathpartir}
\usepackage{fullpage}
\usepackage{ifpdf}
\usepackage{graphicx}
%\usepackage[usenames,dvipsnames]{color}
\usepackage{subcaption}
\usepackage{stmaryrd}
%\usepackage[numbers]{natbib}
\usepackage{amsthm}
\usepackage{listings}          % format code
\usepackage{xspace}

% Math mode
%-----------
\newenvironment{nop}{}{}
\newenvironment{smathpar}{
\begin{nop}\small\begin{mathpar}}{
\end{mathpar}\end{nop}\ignorespacesafterend}

% Name
%-----
\newcommand{\name}{{\sf DaLi}\xspace}

% Formatting
%---------
\newcommand{\C}[1]{\code{#1}}
\newcommand{\tuplee}[1]{\langle #1 \rangle}
\newcommand*{\rom}[1]{\expandafter\romannumeral #1}

% Formatting commands
% -------------------
\newcommand{\code}[1]{\,{\tt #1}\,}
\newcommand{\spc}[0]{\quad}
\newcommand{\ALT}{~\mid~}
\newcommand{\rel}[1]{{R}_{\mathit{#1}}}
\newcommand{\conj}{~\wedge~}
\newcommand{\disj}{~\vee~}
\newcommand{\rulelabel}[1]{\textrm{\sc {#1}}}
\newcommand{\ilrulelabel}[1]{{\sc #1}}
\newcommand{\RULE}[2]{\frac{\begin{array}{c}#1\end{array}}
                           {\begin{array}{c}#2\end{array}}}
\newcommand{\denot}[1]{\llbracket #1 \rrbracket}
\newcommand{\bind}{>\!\!>\!\!=}
\newcommand{\coloneqq}{::=}
\newcommand{\stepsto}{\longrightarrow}
\newcommand{\return}[1]{\C{return}\;#1}
\newcommand{\run}[2]{\C{run}\;#1\;#2}
\newcommand{\fork}[1]{\C{fork}\;#1}
\newcommand{\push}[1]{\C{push}\;#1}
\newcommand{\pull}{\C{pull}}
\newcommand{\semsucceq}{\succeq_{\circ}}
\newcommand{\sempreceq}{\preceq_{\circ}}
\newcommand{\under}[2]{#1\,\vdash\,#2}
\newcommand{\mbleto}{\rightsquigarrow_m}

% New colors
%------------
\definecolor{Bittersweet}{rgb}{1.0, 0.44, 0.37}

% Listings Code
%---------------
\newcommand{\lstml}{
\lstset{ %
language=ML, % choose the language of the code
basicstyle=\small\ttfamily,       % the size of the fonts that are used for the code
keywordstyle=\color{Bittersweet},
% numbers=left,                   % where to put the line-numbers
numberstyle=\tiny,      % the size of the fonts that are used for the line-numbers
stepnumber=1,                   % the step between two line-numbers. If it is 1 each line will be numbered
numbersep=5pt,                  % how far the line-numbers are from the code
showspaces=false,               % show spaces adding particular underscores
showstringspaces=false,         % underline spaces within strings
showtabs=false,                 % show tabs within strings adding particular underscores
% frame=single,                   % adds a frame around the code
tabsize=2,                      % sets default tabsize to 2 spaces
captionpos=b,                   % sets the caption-position to bottom
breaklines=true,                % sets automatic line breaking
breakatwhitespace=false,        % sets if automatic breaks should only happen at whitespace
commentstyle=\itshape\color{MidnightBlue},
%escapeinside={\%*}{*)},         % if you want to add a comment within your code
morekeywords={module, @@deriving, not, : , /\\}
}}
\lstnewenvironment{ocaml}
    { % \centering
			\lstml
      \lstset{}%
      \csname lst@setfirstlabel\endcsname}
    { %\centering
      \csname lst@savefirstlabel\endcsname}

@@

\input{motivation}

\input{semantics}
